\LaTeX\ Author Guidelines for 3DIMPVT Proceedings

### 2012-06-17 3dimpvt/paper.tex
updating

%%%%%%%%% ABSTRACT
\begin{abstract}
  Automated 3D modeling of building interiors is used in applications
  such as virtual reality and environment mapping. Texture mapping
  these models accurately is vital towards visualizing the data
  gathered by modeling systems and increases overall usability. The
  localization of cameras in 3D scenes often suffers from
  inaccuracies, resulting in visible discontinuties when different
  images are projected onto a texture. Previous approaches at
  minimizing these discontinuities suffer from error accumulation when
  stitching together multiple images and do not robustly handle wide
  ranges of camera locations and angles. We propose two approaches for
  reducing discontinuities during texture mapping, tailored towards a
  backpack-mounted data acquisition system.
\end{abstract}

@@

The aim of this paper is to present a solution for texture mapping the
3D models generated by indoor modeling systems, with specific
attention given to a human-operated system with higher localization
errors and greater variance in camera locations. The paper is
organized as follows. Section 2 provides an overview of the backpack
modeling system from which data and examples used throughout this
paper are from. Section 3 describes the general problem of 3D texture
mapping and reviews existing approaches. Section 4 describes
challenges posed by the backpack modeling system and presents our two
approaches tailored for walls and floors/ceilings
respectively. Section 5 compares results and presents conclusions.

\section{Backpack Modeling System}
Human-operated data acquisition systems provide unique advantages in terms of agility and portability over vehicular-mounted systems. Unfortunately, human-operated systems suffer from a lack of automation and stability, resulting in higher localization variance and leading to the problems discussed in Section 4.

\subsection{Data Acquisition Hardware}
The backpack modeling system from which our data was collected contains five 2D laser range scanners, two cameras, an orientation sensor, and an IMU (Should I even mention the IMU at all?). The laser scanners are 40Hz Hokuyo UTM-30LX 2D laser scanners with a 30-meter range and a 270$^{\circ}$ field of view. These scanners are mounted orthogonally to one another. The two cameras are Point Grey Grasshopper GRAS-50S5C units equipped with fisheye lenses, resulting in a 180$^{\circ}$ field of view. The IMU, a Honeywell HG9900, is a strap-down navigation-grade sensor which combines three ring laser gyros with bias stability of less than 0.003$^{\circ}$/hour and three precision accelerometers with bias of less than 0.245mm/sec$^{2}$. The HG9900 provides highly accurate measurements of all 6 DOF at 200Hz and thus serves as our ground truth for the experiments in this paper. ]The orientation sensor (OS), an InterSense InertiaCube3, provides orientation parameters at a rate of 180Hz.

\subsection{Environment Reconstruction}
Using a combination of these sensors and multiple localization and loop-closure algorithms, the backpack is localized over its data collection period, and a 3D point cloud of our environment is constructed. Approximate normal vectors for each point in the point cloud are then calculated by gathering neighboring points within a small radius and running a Principal Component Analysis procedure. These normal vectors allow for the classification and grouping of adjacent points into structures such as walls, ceilings, floors, and staircases. A RANSAC algorithm is then employed to fit polygonal planes to these structured groupings of points, resulting in a fully planar model. This planar model, consisting of multiple 2D polygonal planes in 3D space, along with the set of images captured by the backpack's camera, can be considered the input data on which our approach runs.

\subsection{Image Subsampling}
Before beginning the texture mapping process, it is prudent to reduce the amount of potential images being considered for texture mapping each plane. The backpack modeling system takes 5 pictures/second from both cameras, resulting in each plane being present in (and capable of being textured mapped by) thousands of images, at a wide variance of distances and angles. Thus, for the sake of efficiency, it makes sense to associate each plane with a much smaller sample of images. When creating this subset of images for each plane, there are three criteria we keep in mind. First, we want such a subset of images to be capable of texturing the entirety of a plane, so as to ensure there are no holes in our final texture. Second, we want all our images to be taken from a relatively close distance to the plane, and at as much of a direct, head-on angle as possible. This ensures that the image projects squarely onto our desired plane, with minimal inclusion of other planes, and we get a texture with high resolution. Third, we desire an amount of overlap between the images chosen. This overlap helps us with preprocessing as well as postprocessing techniques discussed in Sections x and y.

To meet these three criteria, we tesselate each plane into [X] triangles of [Y] size. For each triangle, we find all images that can be projected upon the entirety of the triangle, accounting for occlusion with other planes as well, using standard ray-polygon intersection tests. Of these images, we then select the best one according to the heuristic in equation X, favoring closer distances and more head-on viewing angles. We also enforce that no two images are chosen such that they were taken within 0.5 meters of eachother. This results in a greatly-reduced set of images such that each one is objectively the "best" location-wise for some number of areas on the plane, addressing the first two criteria. Furthermore, since cameras are only at good angles to triangles near their center of projection, images will be chosen such that there is high overlap between them. This process reduces the amount of candidate images for each plane from many thousands to around 50, at fairly even spacing. With this completed, each of our planes is associated with a sufficiently sized list of candidate images, and we are ready to begin texture mapping.

\section{NOTES}
4 Special Considerations due to BMS blabla sucky title
The backpack modeling system described in Section 2 was designed to prioritize for texturing walls. As mentioned previously, the backpack contains two fisheye cameras, one aimed directly to the left of the backpack operator, and one aimed directly to the right. Thus, in order to texture the ceiling where the operator walked, images from both cameras must be combined. Even more problematic, the floor beneath the backpack is physically obscured by the operator's body, and thus must be textured by images taken from different locations. These problems are compounded by the fact that the operator's data acquisition path attempts to fully scan each wall, but not necessarily the entirety of a floor or ceiling. This means that large swaths of floors and ceilings are never walked directly over or under, and thus must be textured by sidelong images taken from further distances and at oblique angles. We strongly prefer head-on images because when images are projected onto a planar surface at an extreme angle, the resultant texture ends up spanning a large portion of the plane, applying low-resolution textures to areas at a great distance from the camera location.

In short, these factors mean that wall planes are associated with a multitude of upright, uniform images, taken head-on and from a relatively close distance at regular intervals, while floors and ceilings are associated with images of all orientations and distances. This major difference suggests we employ two strategies, one tailored for each scenario.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
  Automated 3D modeling of building interiors is useful in applications
  such as virtual reality and environment mapping. Accurate texture
  mapping of these models is vital towards visualizing the data
  gathered by modeling systems and increases overall usability. The
  localization of cameras in 3D scenes with respect to model surfaces
  often suffers from inaccuracies, resulting in visible discontinuties
  when different images are directly projected onto a plane for
  texturing. Previous approaches at minimizing these discontinuities
  suffer from error accumulation when stitching together multiple
  images and do not robustly handle a wide range of camera locations
  and angles. We propose two approaches for reducing discontinuities
  during texture mapping, tailored towards a backpack-mounted data
  acquisition system.
\end{abstract}

@@

The aim of this paper is to present a solution for texture mapping the
3D models generated by indoor modeling systems, with specific
attention given to a human-operated system with higher localization
errors and greater variance in camera locations. The paper is
organized as follows. Section \ref{sec:backpackSystem} provides an
overview of the backpack modeling system from which data and examples
used throughout this paper are from. Section
\ref{sec:textureMappingOverview} describes the general problem of 3D
texture mapping and reviews existing approaches. Section
\ref{sec:textureMappingMethods} describes challenges posed by the
backpack modeling system and presents our two approaches tailored for
walls and floors/ceilings respectively. Section \ref{sec:results} compares results and
presents conclusions.

\section{Backpack Modeling System}
\label{sec:backpackSystem}
Human-operated data acquisition systems provide unique advantages over vehicular-mounted systems in
terms of agility and portability. Unfortunately, human-operated systems also suffer from a lack of
automation and stability, resulting in higher localization variance
and leading to the problems discussed in Section 4.

\subsection{Data Acquisition Hardware}
The backpack modeling system from which our data was collected
contains five 2D laser range scanners, two cameras, an orientation
sensor, and an IMU. The laser
scanners are 40Hz Hokuyo UTM-30LX 2D laser scanners with a 30-meter
range and a 270$^{\circ}$ field of view. These scanners are mounted
orthogonally to one another. The two cameras are Point Grey
Grasshopper GRAS-50S5C units equipped with fisheye lenses, resulting
in a 180$^{\circ}$ field of view. The IMU, a Honeywell HG9900, is a
strap-down navigation-grade sensor which combines three ring laser
gyros with bias stability of less than 0.003$^{\circ}$/hour and three
precision accelerometers with bias of less than 0.245mm/sec$^{2}$. The
HG9900 provides highly accurate measurements of all 6 DOF at 200Hz, and the orientation sensor (OS), an InterSense InertiaCube3,
provides orientation parameters at a rate of 180Hz.
Wearing this backpack, a human operator then takes great care to walk a path such that every wall in the desired indoor environment is passed and scanned lengthwise at least once.

\subsection{Environment Reconstruction}
Using data gathered by the onboard sensors and multiple localization and
loop-closure algorithms, the backpack is localized over its data
collection period, and a 3D point cloud of the environment is
constructed. Approximate normal vectors for each point in the point
cloud are then calculated by gathering neighboring points within a
small radius and processing them with Principal Component Analysis. These normal vectors allow for the classification and
grouping of adjacent points into structures such as walls, ceilings,
floors, and staircases. A RANSAC algorithm is then employed to fit
polygonal planes to these structured groupings of points, resulting in
a fully planar model. This planar model, consisting of multiple 2D
polygonal planes in 3D space, must then be textured by some subset of the images captured by
the backpack's camera.

\subsection{Plane Generalization}
The planes we aim to texture are output by the surface reconstruction
algorithm briefly explained in Section \ref{sec:backpackSystem}.
These planes have arbitrary orientation and include simple rectangular
walls as well as complicated floor planes defined by over 100
vertices. In order to abstract out the difficulties of dealing with
complex geometry, a minimal bounding box is constructed for each
plane, and used as the target for texture mapping. Since the final
texture created will be a standard rectangular image regardless, we
can simply leave the area between the plane boundary and its bounding
box untextured, and make sure to store the plane's original vertices
for future retrieval.

\subsection{Image Association}
\label{sec:imageAssociation}
In order to speed up the texture mapping process, it is prudent to
reduce the amount of potential images being considered for texture
mapping each plane. The backpack modeling system takes 5
pictures/second from both cameras, resulting in each plane being
present in (and capable of being textured mapped by) thousands of
images, at a wide range of distances and angles. Thus, for the sake
of efficiency, it makes sense to associate each plane with a much
smaller list of images. When creating this subset of images to be associated with each
plane, there are three criteria we keep in mind. First, we want such a
subset of images to be capable of texturing the entirety of a plane,
so as to ensure there are no holes in our final texture. Second, we
want all our images to be taken from a relatively close distance to
the plane, and at as much of a direct, head-on angle as possible. This
ensures that the image projects squarely onto our desired plane, with
minimal inclusion of other planes, and we get a texture with high
resolution. Third, we desire an amount of overlap between the images
chosen. This overlap helps us with preprocessing as well as
postprocessing techniques discussed in Sections x and y.

To meet these three criteria, we divide each plane into [X] triangles
of [Y] size (our planes often have fairly complex geometry, hence the
use of triangulation), using an ear-clipping algorithm followed by
further triangular tesselation. For each triangle, we find all images
that can be projected upon the entirety of the triangle, accounting
for occlusion with other planes as well, using the standard
ray-polygon intersection test shown in figure X. Of these images, we
then select the best one according to the heuristic in equation X,
favoring closer distances and more head-on viewing angles. We also
enforce that no two images are chosen such that they were taken within
0.5 meters of eachother. This results in a greatly-reduced set of
images such that each one is objectively the "best" location-wise for
some number of areas on the plane, addressing the first two
criteria. Furthermore, since cameras are only at good angles to
triangles near their center of projection, images will be chosen such
that there is high overlap between them. With this process completed,
we have reduced the amount of candidate images for each plane from
many thousands to around 50, and are ready to begin the texture
mapping process.

\section{Texture Mapping Overview}
\label{sec:textureMappingOverview}

\begin{figure}
  \centering
  \includegraphics[height=2in]{Projection.pdf}
  \caption{Planes are specified in 3D space by four corners $C_1$ to
    $C_4$. Images are related to each plane through the camera
    matrices $P_{1..M}$. }
  % \caption{The plane is specified in 3D space by the four corners
  % $C_1$ to $C_4$. Images are related to the plane through the camera
  % matrices $P_{1..M}$. For example, the 3D point X in the world
  % coordinate system is related to the image point x shown in the
  % figure as $x = P_i X$.}
  \label{fig:projection}
\end{figure}

In this section, we will discuss the process of texture mapping a
single plane, as the texturing of each of our planes is completely
independent and can even be completed in parallel.

The geometry of the general texture mapping process is shown in Figure 1.

 As
described in the previous section, we are provided with a set of $M$
candidate images for each plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
translates a 3D point in the world coordinate system to a 2D point in
image $i$'s coordinates. A camera matrix $P_i$ is composed of the
camera's intrinsic parameters, such as focal length and image center,
as well as the extrinsic parameters which specify the rotation and
translation of the camera center's position with respect to the world
coordinates at the time that image $i$ was taken. These extrinsic
parameters are determined by the localization hardware and algorithms
mentioned in Section \ref{sec:backpackSystem}. A point $X$ on the
plane in 3D space can be related to its corresponding pixel $x$ in image $i$
through the following equation:

\[
x=project(P_iX)
\]

where
\[X = \begin{pmatrix} x \\ y \\ z \end{pmatrix} \textrm{ and }
project(X) = \begin{pmatrix} x/z \\ y/z \end{pmatrix}
\]

A plane to be textured is defined by four corner vertices $C_1$ to $C_4$ in
world coordinates and a normal vector indicating the front facing side
of the plane. Our goal is to texture this plane using its associated
images, while eliminating any visual discontinuities or seams that
would suggest that the plane's texture was not composed of a single
continuous image.

\subsection{Naive Mapping}
\label{sec:naive}
\begin{figure}
  \centering
  \includegraphics[height=1.5in]{naive.png}
  \caption{The result of naive texture mapping based on the imprecise
    camera matrices estimated by the localization system.}
  \label{fig:naive}
\end{figure}

Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
one can texture map the plane simply by discretizing the plane into
sections and texturing each section with one image. It makes sense to
texture each section by selecting the best image locally, as was done
in \ref{sec:imageAssociation}.

As Figure \ref{fig:naive} demonstrates, this naive mapping approach
leads to significant misalignment between successive tiles. This
suggests that while the errors in the localization system are quite
low, they are not pixel accurate. For photorealistic texture mapping,
either the camera matrices need to be refined such that the
localization is pixel accurate, resulting in a perfect mapping, or
image stitching techniques need to be applied to provide this
illusion. A commonly-used technique for each approach is examined
next.

\subsection{Image Mosaicing}

\begin{figure}
  \centering
  \includegraphics[width=3in]{panoMy.jpg}
  \caption{Image mosaicing. }
  \label{fig:mosaic}
\end{figure}

When images are taken of a plane from arbitrary overlapping positions,
they are related by homography \cite{hz}. Thus, existing
homography-based image mosaicing algorithms are applicable
\cite{brown2007automatic}. However, errors can compound when long
chains of images are mosaiced together using these approaches. For
example, a pixel in the $n$th image in the chain must be translated
into the first image's coordinates by multiplying by the $3\times3$
matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these homography
matrices is propagated to all further images until the chain is
broken. For some chains of images this can happen almost immediately
due to erroneous correspondence matches and the resulting image mosaic
is grossly misshapen.

Figure \ref{fig:mosaic} shows the output of the AutoStitch software
package which does homography-based image mosaicing. This plane is
nearly a best-case scenerio with many features spread uniformly across
it. Even so, the mosaicing produces errors that causes straight lines
to appear as waves on the plane. This image was generated after
careful hand tuning. Many planes that had fewer features simply
failed. This led to the conclusion that image mosaicing is not a
robust enough solution for reliably texture mapping our dataset.

\subsection{Image-Based 3D Localization Refinement}

\begin{figure}
  \centering
  \includegraphics[width=3in]{Graph_crop.pdf}
  \caption{Using the graph-based localization refinement algorithm
    from [11] suffers from the problem of compounding errors. }
  \label{fig:graph}
\end{figure}

Another approach is to refine the camera matrices using image
correspondences to guide the process. Each image's camera matrix has 6 degrees of freedom. Previous work has attempted to refine
camera matrices by solving a non-linear optimization problem
\cite{liu2010indoor}. This process is specific to the backpack system
which generated our dataset, as it must be run during backpack
localization\cite{liu2010indoor,chen2010indoor}. Unfortunately, this
approach suffers from a similar error propagation problem shown in
Figure \ref{fig:graph}. In our new approach, we also refine the
placement of images using image correspondences. However, we do so in
two dimensions on the plane whereas this previous work did so over all
6 degrees of freedom. Refining in two dimensions on the plane is less
flexible in that it does not address projection errors, however, it
provides noticeable benefits while avoiding the error propagation
problem.

\section{Our Approach}
Our approach begins with the naive projection of all our images onto separate copies of our plane, such that no projected data is lost. We then perform a series of preprocessing steps to rotate and shift each image's projection such that its overlapping regions with other projections are as seamless as possible. Following this, we perform a basic intensity-matching algorithm across all images, as images taken from different locations have different levels of overall brightness. From here, we assign textures to our planes using one of two methods, dependent on whether they are wall planes or ceiling/floor planes. The reasoning for this is explained in section \ref{sec:whydifferent}. Lastly, we apply alpha blending to smooth out any remaining seams.

\subsection{Preprocessing}
As a starting point, we naively texture map the plane using the given imprecise camera matrices for each image in the set. This is done by discretizing the plane into an arbitrary density of pixels and projecting each pixel into the image plane using the estimated camera matrix $P_i$. We later intend to shift some of these projected images around on the plane and remove some others. Therefore, each image is stored intact in its own data structure so that it can later be merged with the other images on the plane. We use a Hough transform to rotate the projected images such that vertical lines are pointing directly upwards. This can be effective for indoor modeling, since many indoor scenes contain strong vertical lines from features such as doors, wall panels, or rectangular frames.

\subsection{Localization Refinement}

The camera matrices generated by the localization algorithm are imprecise so the images are misaligned. To fix this, we choose to fix the locations in 2D. First we find corresponding points between all pairs of overlapping images using SIFT matches \cite{lowe1999object}. An illustration of this is given in Figure \ref{fig:matches}. The SIFT matches allow us to determine the correct $x$ and $y$ distances between two images on the plane. We already have an estimate of the $x$ and $y$ distances between the two images which was given by the localization algorithms. Soon we will compare the original estimates to the SIFT-based distances and use this to improve the quality of the image locations.

\subsubsection{Robust SIFT Distances using RANSAC}

First we need to ensure that the SIFT-based distances are reliable. Since SIFT matches frequently include outliers, the RANSAC framework \cite{fischler1981random} is used for a robust estimate of the $x$ and $y$ distances between the two images. The RANSAC framework will attempt to build a consensus among the SIFT matches about what the true $x$ and $y$ distance is between the two images while ignoring the influence of outliers that may skew the results. The framework handles the consensus-building machinery, and only requires that two functions be specified: the fitting function and the distance function. These functions are called for random subsets of the SIFT matches until the best set of inliers is found. For this application, the fitting function simply finds the average distance between matches. If the matches are exactly correct and the image is frontal and planar then the distances for various SIFT feature matches should be the same. Our distance function for a pair of points is the difference between those points' SIFT match distance and the average distance computed by the fitting function. We specified a 10 pixel outlier threshold to the framework. This means that a SIFT match is labeled as an outlier if its $x$ and $y$ distance is not within 10 pixels of the average distance computed by the fitting function.

\subsubsection{Refining Image Positions using Least Squares}

There are a total of $M^{2}$ possible pairs of images, however we can only measure distances between images that overlap at SIFT feature points. Given these distances and the original image location estimates, we solve a least squares problem ($\textrm{min}_{\beta} ||\beta X - y||_2^2 $) to estimate the correct location of the images on the plane. The vector $\beta$ of unknowns are the correct $x$ and $y$ locations of each image on the plane from $1 \dots M$. Finding the correct $x$ and $y$ locations are independent from one another so we will only consider the $x$ locations:

% Draw least squares problem here.

\[\beta =
 \begin{pmatrix}
  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
 \end{pmatrix}
\]

The matrix $X$ is constructed with one row for each pair of images with measured distances produced by the SIFT matching stage. A row in the matrix has a $-1$ and $1$ in the columns corresponding to the two images in the pair. For example, the matrix below indicates that we generated a SIFT-based distance between images 1 and 2, images 1 and 3, images 2 and 3, etc.

\[
 X =
 \begin{pmatrix}
  -1 & 1 & 0 & \cdots & 0 & 0\\
  -1 & 0 & 1 & \cdots & 0 & 0\\
   0 & -1 & 1 & \cdots & 0 & 0\\
  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
  0 & 0 & 0 & \cdots & 1 & 0 \\ 
  0 & 0 & 0 & \cdots & -1 & 1 \\ 
  1 & 0 & 0 & \cdots & 0 & 0 \\ 
 \end{pmatrix}
\]

If only relative distances between images are included then there is no way to determine the absolute location of any of the images and the matrix becomes rank deficient. To fix this we choose the first image to serve as the anchor for the rest, meaning all the absolute distances are based on its original location. This is done by adding a row with a $1$ in the first column and the rest zeros.

Finally, the observation vector $y$ is constructed using the SIFT-based distances generated earlier in the matching stage. The distances are denoted as $d_1 \dots d_N$ for $N$ SIFT-based distances. The last element in the observation vector is the original location of the first image determined by the localization algorithm.

\[
y^T = 
 \begin{pmatrix}
  d_{1,2}, & d_{1,3}, & d_{2,3}, & \hdots & d_{N-2,N-1}, & d_{N-1,N}, &  x_1
 \end{pmatrix}
\]

The $\beta$ that minimizes  $||\beta X - y||_2^2$ tells us a set of image locations on the plane that best honors all the SIFT-based distance measurements between images. A similar problem is solved for the $y$ dimension. In practice there are often cases where there is a break in the chain of images, meaning that no SIFT matches were found between one segment of the plane and another. In this case we add rows to the $X$ matrix and observations to the $y$ vector that contain the original $x$ and $y$ distance estimates generated by the localization algorithm. Another way to do this is to add rows for all neighboring pairs of images and solve a weighted least squares problem where the SIFT distances are given a higher weight i.e. 1, and the distances generated by the localization algorithm are given a smaller weight i.e. 0.01.

At this point we now have our target plane associated with a list of images as well as their rotated and shifted projections upon the plane. We are ready to begin assigning these projections to areas of our plane for texturing.

\subsection{Ceiling/Floor Texturing vs. Wall Texturing}
\label{sec:whydifferent}
The backpack
modeling system described in Section \ref{sec:backpackHardware} was designed to prioritize for
texturing walls. As mentioned previously, the backpack contains two
fisheye cameras, one aimed directly to the left of the backpack
operator, and one aimed directly to the right. Thus, in order to
texture the ceiling above where the operator walked, images from both
cameras must be combined, with their boundaries meeting overhead. Even more problematic, the floor beneath the
backpack is physically obscured by the operator's body, and thus must
be textured by images taken from behind the operator or from the side. This problem of distant cameras at poor angles
is compounded by the fact that the operator's data acquisition path
attempts to fully scan each wall, but not necessarily the entirety of
a floor or ceiling. This means that large swaths of floors and
ceilings are never walked directly over or under, and thus must be
textured by sidelong images taken from further distances and at
oblique angles. Images taken from closer distances are much preferred, as the effects of imprecise localization and camera matrices become multiplied over greater distances. We also strongly prefer head-on images because when images
are projected onto a planar surface at an extreme angle, the resultant
texture ends up spanning a large portion of the plane, applying
low-resolution textures to areas at greater distances from the camera
location.

In short, these factors mean that wall planes are generally associated with a
multitude of upright, uniform images, from a relatively close distance and originally taken head-on at regular intervals, while floors and
ceilings are associated with images taken from all manner of orientations and
distances. This major difference suggests we employ two strategies,
one tailored for each scenario.

\subsection{Texturing Walls}
Because wall images in general are all good candidates for texturing due to their orientation and location, our goal is less about selecting good images for individual texturing, and more about selecting a set of images that together form a good texture.

\subsection{Texturing Ceilings and Floors}

Because the images associated with ceilings and floors are often captured by cameras at sidelong angles, we must be conservative when texture mapping such planes. Since localization errors compound over distance, we often have candidate images that project well on areas near the camera itself, but much more poorly at greater distances.

Furthermore, as a result of the projection process and cropping due to occlusion, The geometry of the usable texture projected onto the plane for each image is generally complex and difficult to work with.

These problems suggest that we must segment our images to some extent, as many of our images have desired as well as undesired portions. Such segmentation undoubtedly leads to more discontinuities, but floors and ceilings have lame textures

\subsection{Evaluation of Methods}
methods can be used on eachother

\section{NOTES}

\subsection{Occlusion Masking}
not sure where this section should go. it happens after projections,
discussed in texture mapping overview, but it's definitely more of a
preprocessing step.  Before we proceed with texturing our planes, we
need to ensure that each plane's associated images contain only
content that should be mapped onto the target plane in question. From
the above process, images were chosen such that they had an unoccluded
view of one or more trianglular sections upon a plane. This may not
necessarily hold true however for all areas of the plane, as
demonstrated in figure SOMETHING. If images are not modified to mask
out occluded areas, different images could attempt to cover the same
location on a plane with drastically different textures, inevitably
leading to undesireable discontinuities in our final texture.

Fortunately, by virtue of our indoor environments, the vast majority
of surface geometry is either horizontal or vertical, with high
amounts of right angles. This means that the areas we wish to mask out
of our images due to occlusion are nearly always rectangular
areas. Similar to the triangular tesselation performed for image
association above, we split our image into

With the steps in this section completed, we have generalized the
input of our texture mapping problem into rectangular planes that are
associated with a list of good candidate images, and we are ready to
begin the texture mapping process.
